### 2020-08-17 evaluation.tex
typo

\section{Model Evaluation}
\label{sec-evaluation}
% \begin{figure*}[!t]
%     \centering
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
%     \hfill
%     \caption{Performance in Controlled Environment (a,b) and Random Environment (c,d).}
%     \label{fig-performance-1}
% \end{figure*}
We perform the following experiments with two commercial off-the-shelf(COTS) smartphones: a Redmi 6A smartphone, with a single rear camera with 13 million pixels and digital zoom only, and a HUAWEI P40 Pro, with multiple rear cameras. The telephoto camera possesses up to 5$\times$ optical zooming ability which we will utilize fully in our experiments. The Peak Signal to Noise Ratio(PSNR) metric and Optical Character Recognition (OCR) services are used to evaluate the accuracy of our system.

@@

\subsection{Performance with Fewer Available Images}
As mentioned in sec.~\ref{sec-design}, our model is designed to work on any number of input images, which is requisite because in certain scenarios the data displayed on the victim's screen is transient and ever-changing, e.g. password entry. The previous experiments are all conducted with the ideal 20 frames per burst, but in the case study at Sec.~\ref{case-study} and real-life scenarios the attacker only gets to photograph when the screen display remains constant, so there might be fewer images available. We evaluated the impact of fewer available images on the performance of the SR model. The results are shown in fig.~\ref{fig:number_adapting}. We tested at the 1.8m daytime scenario for traditional lens and 6m daytime scenario for optical lens.

@@

\subsection{Adapting Ability}
We train the model with fewer groups of data, exposing it to fewer variations of a certain environment parameter when training, and examine the model's performance in random environments. The results are shown in Figure~\ref{fig:number_adapting}.

>>>>

\section{Model Evaluation}
\label{sec-evaluation}
% \begin{figure*}[!t]
%     \centering
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
%     \hfill
%     \caption{Performance in Controlled Environment (a,b) and Random Environment (c,d).}
%     \label{fig-performance-1}
% \end{figure*}
We perform the following experiments with two commercial off-the-shelf(COTS) smartphones: a Redmi 6A smartphone, with a single rear camera with 13 million pixels and digital zoom only, and a HUAWEI P40 Pro, with multiple rear cameras. The telephoto camera possesses up to 5$\times$ optical zooming ability which we will utilize fully in our experiments. The Peak Signal to Noise Ratio(PSNR) metric and Optical Character Recognition (OCR) services are used to evaluate the accuracy of our system(the latter using accuracy per character).

@@

\subsection{Performance with Fewer Available Images}
As mentioned in sec.~\ref{sec-design}, our model is designed to work on any number of input images, which is requisite because in certain scenarios the data displayed on the victim's screen is transient and ever-changing, e.g. password entry. The previous experiments are all conducted with the ideal 20 frames per burst, but in the case study at Sec.~\ref{case-study} and real-life scenarios the attacker only gets to photograph when the screen display remains constant, so there might be fewer images available. We evaluated the impact of fewer available images on the performance of the SR model. The results are shown in fig.~\ref{fig-image-tranditional-2} and fig.~\ref{fig-image-optical-2}. We tested at the 1.8m daytime scenario for traditional lens and 6m daytime scenario for optical lens.

@@

\subsection{Adapting Ability}
We train the model with fewer groups of data, exposing it to fewer variations of a certain environment parameter when training, and examine the model's performance in random environments. The results are shown in fig.~\ref{fig-adapt-tranditional} and fig.~\ref{fig-adapt-optical}.

### 2020-08-17 introduction.tex
typo

\textbf{Motivation.} Although it's pointed out by Eiband~\cite{eiband2017understanding} that in most occasions the shoulder surfer means no harm and merely takes several peeks out of curiosity, we argue that a mere stranger can hardly do any harm, and it is the rare but malicious attacker, with certain familiarity and knowledge of the victim, that can utilize the stolen information and should be the primary object of our defenses.
%The attacker can even be our children stealing electronic payment passwords and spending huge sums in their games~\cite{2017childsteal}. 
The argument goes the same with smartphones---although uncommon, the utilization of this commonly available equipment can deal much greater harm with longer attacking range and ability to preserve evidence. For example, in a Senate hearing, the Justice Secretary of the Philippines, Vitaliano Aguirre II, suffered a leakage of his text messages, as someone had taken a snapshot of his smartphone \cite{Polotiko2017leakage}. 
The privacy concerns have been exacerbated by the rapidly developed mobile camera module these years. Equipped with multiple cameras, the newest generation of smartphones can perform 100$\times$ zooming compared to the standard 5$\times$ of single camera phones. Hardware improvements in memory also allow the burst mode at tremendous frame rates and even high-speed photography, delivering videos with thousands of frames per second, enabling the usage of multi-frame super resolution (SR) algorithms to further improve the shoulder surfing range.

@@

\vspace{1mm}
\noindent
\textbf{Threat Model.} We present \textsf{SRPeek}, an end-to-end system of shoulder surfing using the SR algorithm, illustrated in Figure~\ref{overview}. 
While the victim's reading private information in public, the attacker, given that he/she has acquired line of sight of the screen, uses his commercial smartphone to take 10 to 20 snapshots rapidly in burst mode (about 10 frames per second), and processes the images with multi-frame SR algorithms to generate a high-resolution result. The whole process only takes a few seconds and can even be repeated at a 2 second interval, enabling the attacker to monitor the victim's screen continuously. Meanwhile, few people would suspect a stranger holding his smartphone at 1.8 meters behind them. Given the newest generation of smartphones equipped with telephoto lenses and capable of optical zooming, this distance can reach a staggering 6 meters, posing a silent but deadly threat to screen privacy.

\vspace{1mm}
\noindent
\textbf{Challenges.} Creating a powerful SR based shoulder surfing threat model, however, is not trivial, especially for commercial smartphones in real time. And we achieve \textsf{SRPeek} by overcoming four key challenges.

>>>>

\textbf{Motivation.} Although it's pointed out by Eiband~\cite{eiband2017understanding} that in most occasions the shoulder surfer means no harm and merely takes several peeks out of curiosity, we argue that a mere stranger can hardly do any harm, and it is the rare but malicious attacker, with certain familiarity and knowledge of the victim, that can utilize the stolen information and should be the primary object of our defenses.
%The attacker can even be our children stealing electronic payment passwords and spending huge sums in their games~\cite{2017childsteal}. 
The argument goes the same with cameras---although uncommon, the utilization of this commonly available equipment can deal greater harm with longer attacking range and ability to preserve evidence. Furthermore, the vulnerable information is not limited to passwords, as although biometrics and login services can conceal passwords from screens, leakage of texts and emails can also be perilous. For example, in a Senate hearing, the Justice Secretary of the Philippines, Vitaliano Aguirre II, suffered a leakage of his text messages, as someone had taken a snapshot of his smartphone \cite{Polotiko2017leakage}. 
The privacy concerns have been exacerbated by the rapidly developed mobile camera module these years. Equipped with multiple cameras, the newest generation of smartphones can perform 100$\times$ zooming compared to the standard 5$\times$ of single camera phones. Hardware improvements in memory also allow the burst mode at tremendous frame rates and even high-speed photography, delivering videos with thousands of frames per second, enabling the usage of multi-frame super resolution (SR) algorithms to further improve the shoulder surfing range.

@@

\vspace{1mm}
\noindent
\textbf{Threat Model.} We present \textsf{SRPeek}, an end-to-end system of shoulder surfing using the SR algorithm, illustrated in Figure~\ref{overview}. 
While the victim's reading private information in public, the attacker, given that he/she has acquired line of sight(LoS) of the screen, uses his commercial smartphone to take 10 to 20 snapshots rapidly in burst mode (about 10 frames per second), and processes the images with multi-frame SR algorithms to generate a high-resolution result. The whole process only takes a few seconds and can even be repeated at a 2 second interval, enabling the attacker to monitor the victim's screen continuously. Meanwhile, few people would suspect a stranger holding his smartphone at 1.8 meters behind them. Given the newest generation of smartphones equipped with telephoto lenses and capable of optical zooming, this distance can reach a staggering 6 meters, posing a silent but deadly threat to screen privacy.

\vspace{1mm}
\noindent
\textbf{Challenges.} Creating a powerful SR based shoulder surfing threat model, however, is not trivial, especially for commercial smartphones in real-time. And we achieve \textsf{SRPeek} by overcoming four key challenges.

### 2020-08-17 system_overview.tex
typo

\vspace{1mm}
\noindent
\textbf{Adjustment:} The lines of text(or stuff differing from the background color of the screen) will be carved out for processing to reduce the workload of the network. The character size is normally 10 to 20 pixels, while variations in size aren't influential as they're covered in the training data, so zooming isn't necessary.

@@

These steps are repeatedly executed to enable the attacker to monitor the victim at an interval of 1 to 2 seconds. At critical times requiring continuous monitoring so as not to miss transient display, e.g. password entering, the system can simply lengthen the input phase across that period and process the data later. The workflow of our system is shown in Figure~\ref{fig-workflow}.
\begin{figure}
  \centering
     \includegraphics[width=0.90\linewidth]{./pic/workflow_cl.pdf}
     \caption{Workflow of the \textsf{SRPeek} system.}
     \label{fig-workflow}
\end{figure}

>>>>

\vspace{1mm}
\noindent
\textbf{Adjustment:} The patches differing from the background color of the screen will be carved out for processing to reduce the workload of the network. The character size is normally 10 to 20 pixels, while variations in size aren't influential as they're covered in the training data, so zooming isn't necessary.

@@

These steps are repeatedly executed to enable the attacker to monitor the victim at an interval of 1 to 2 seconds. If continuous monitoring is required to avoid missing the transient display, e.g. password entering, the system can simply lengthen the input phase across that period and process the data later. The workflow of our system is shown in Figure~\ref{fig-workflow}.
\begin{figure}
  \centering
     \includegraphics[width=0.90\linewidth]{./pic/workflow_cl.pdf}
     \caption{Workflow of the \textsf{SRPeek} system.}
     \label{fig-workflow}
\end{figure}
